\LARGE Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-10-11 poster/main.tex
update plots color

\begin{block}{Objectives}
% \begin{columns} % Subdivide the first main column
% \begin{column}{.69\textwidth}
\begin{enumerate}
\item Designing a differentially private Bayesian inference mechanism.
\item Measuring accuracy with a metric over distributions (Hellinger distance ($\hellinger$)), $f$-divergence, etc.
% \item Calibrating the noise w.r.t sensitivity of the (Hellinger distance).
% \item Applying smooth sensitivity in mechanism to achieve better accuracy.
%         (Fig. \ref{fig_sensitivity} shows that local sensitivity of Hellinger distance is very steep and much higher in the edges but very smooth in central part).
\end{enumerate}
% \end{column}
% \begin{column}{.28\textwidth}
% \begin{figure}[ht]
% \centering
% \includegraphics[width=0.85\textwidth]{poster_0.eps}
% say something about beta...
% \caption{\footnotesize{Local sensitivity of Hellinger}}
% \label{fig_sensitivity}
% \end{figure}
% \vspace{.1cm}
% \end{column}
% \end{columns}

@@

\begin{block}{Differentially Private Bayesian Inference and Motivations}
Releasing a differentially private posterior $\betad (\tilde\alpha,\tilde\beta)=(\alpha +  \widetilde{\Delta \alpha},\beta + n - \widetilde{\Delta \alpha})$.
\begin{columns} % Subdivide the first main column
\begin{column}{.69\textwidth}
\begin{enumerate}
  \item  Baseline approach is Laplace mechanism (LapMech) with sensitivity proportional to $\ell_1$ norm. But we measure results by a different metric and sensitivity grows linear with the dimension. Motivated by this, we calibrate the noise w.r.t sensitivity of the accuracy metric ($\hellinger$). %(v.s. the $\ell_1$ norm in baseline approach).} \todo{} % \todo{give formula of hellinger Distance, give the Dirichlet distribution, no need to formal expression, Laplace with mean and scale in 2 dimension.}
  \item Maximum sensitivity of $\hellinger$ over $\betad$ distributions achieve value at edge as in Fig. \ref{fig_sensitivity}. But it's very low when move away from edge. Motivated by this, we apply smooth sensitivity in mechanism to improve accuracy.
  %{sensitivity is maximize when plot of hellinger distance of alpha and beta variance between adjacent data bases, of varying }
\end{enumerate}
\end{column}
\begin{column}{.28\textwidth}
\begin{figure}[ht]
\centering
\includegraphics[width=0.9\textwidth]{poster_0.eps}
\caption{\footnotesize{Sensitivities of $\hellinger$ over $\betad$}}
\label{fig_sensitivity}
\end{figure}
% \vspace{.1cm}
\end{column}
\end{columns}

@@

\begin{block}{Preliminary Experimental Results}
% Two groups of experimental results both with unit prior $\betad(1,1), \betad(1,1,1)$ and $\betad(1,1,1,1)$, balanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$.
Experiments are on three mechanisms and plotted as follows:
\begin{itemize}
  \item[-] Green: Baseline approach. (noises being postprocessed to floor value) %adds noise scaled to sensitivity proportional to dimensionality,
  \item[-] Red: LapMech adding noise with sensitivity $1$ in 2 dimensions and $2$ in higher dimensions, since it's equivalent to histogram problem 
  (posteriors of adjacent data differ only in two dimensions).
  \item[-] Blue: $\hexpmech$.
\end{itemize}
  Fig. \ref{fig_sampling} and Fig. \ref{subfig_prior} give us the average and 4-quantile of Hellinger distance between the sampled results and true posterior, by sampling for $10k$ times under each data size or prior configuration.

@@

Fig. \ref{subfig_concrete_prob_2d} and \ref{subfig_concrete_prob_3d} give us the discrete probabilities. On the x-axis: the distance of a potential output r from the true answer and on y-axis the probability of r being output by the mechanisms.
\begin{figure}[H]
\begin{center}
\centering
   \subfigure[2 dimensions with data size $100$]{
    \includegraphics[width=0.31\textwidth]{poster_4.eps}
  \label{subfig_prior}
  }
  \subfigure[2 dimensions]{
    \includegraphics[width=0.311\textwidth]{poster_5.eps}
  \label{subfig_concrete_prob_2d}
  }
  \subfigure[3 dimensions]{
    \includegraphics[width=0.311\textwidth]{poster_6.eps}
  \label{subfig_concrete_prob_3d}
  } 
\caption{4-quantile and discrete probability plots}
\label{fig_concrete_prob}
\end{center}
\end{figure}
\scriptsize{Experiments above are with unit prior $\betad(1,1), \betad(1,1,1)$ and $\betad(1,1,1,1)$ (except Fig. \ref{subfig_prior}) , balanced datasets, $\epsilon = 1.0$ and $\delta = 10^{-8}$.}
\end{block}

@@

\begin{itemize}
  \item[-] The smoothed Hellinger distance based exponential mechanism outperforms asymptotically the baseline 
  approach  when the latter uses a sensitivity proportional to dimensionality.
  \item[-] From experimental results, the outperformance happens when the data size is greater than $400$ .
  % \begin{enumerate}
  %   \item  The accuracy that we are going to explore next, and in a more principled and formal way.

>>>>

\begin{block}{Objectives}
% \begin{columns} % Subdivide the first main column
% \begin{column}{.69\textwidth}
\begin{enumerate}
\item Designing a differentially private Bayesian inference mechanism.
\item Measuring accuracy with a metric over distributions (Hellinger distance ($\hellinger$), $f$-divergence, etc.).
% \item Calibrating the noise w.r.t sensitivity of the (Hellinger distance).
% \item Applying smooth sensitivity in mechanism to achieve better accuracy.
%         (Fig. \ref{fig_sensitivity} shows that local sensitivity of Hellinger distance is very steep and much higher in the edges but very smooth in central part).
\end{enumerate}
% \end{column}
% \begin{column}{.28\textwidth}
% \begin{figure}[ht]
% \centering
% \includegraphics[width=0.85\textwidth]{poster_0.eps}
% say something about beta...
% \caption{\footnotesize{Local sensitivity of Hellinger}}
% \label{fig_sensitivity}
% \end{figure}
% \vspace{.1cm}
% \end{column}
% \end{columns}

@@

\begin{block}{Differentially Private Bayesian Inference and Motivations}
Releasing a differentially private posterior $\betad (\tilde\alpha,\tilde\beta)=(\alpha +  \widetilde{\Delta \alpha},\beta + n - \widetilde{\Delta \alpha})$.
\begin{columns} % Subdivide the first main column
\begin{column}{.69\textwidth}
\begin{enumerate}
  \item  Baseline approach is Laplace mechanism (LapMech) with sensitivity proportional to $\ell_1$ norm. But this sensitivity grows linear with the dimension, also we measure results by a different metric. Motivated by this, we calibrate the noise w.r.t sensitivity of the accuracy metric ($\hellinger$). %(v.s. the $\ell_1$ norm in baseline approach).} \todo{} % \todo{give formula of hellinger Distance, give the Dirichlet distribution, no need to formal expression, Laplace with mean and scale in 2 dimension.}
  \item Maximum sensitivity of $\hellinger$ over $\betad$ distributions achieves at edges as in Fig. \ref{fig_sensitivity}. But it's very low when move away from edge. Motivated by this, we apply smooth sensitivity in mechanism to improve accuracy.
  %{sensitivity is maximize when plot of hellinger distance of alpha and beta variance between adjacent data bases, of varying }
\end{enumerate}
\end{column}
\begin{column}{.28\textwidth}
\begin{figure}[ht]
\centering
\includegraphics[width=0.9\textwidth]{poster_0.eps}
\caption{\footnotesize{Sensitivities of $\hellinger$ over $\betad$}}
\label{fig_sensitivity}
\end{figure}
% \vspace{.1cm}
\end{column}
\end{columns}

@@

\begin{block}{Preliminary Experimental Results}
% Two groups of experimental results both with unit prior $\betad(1,1), \betad(1,1,1)$ and $\betad(1,1,1,1)$, balanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$.
Experiments are on three mechanisms and plotted as follows:
\begin{itemize}
  \item[-] Green: Baseline approach. (noises being postprocessed to floor value) %adds noise scaled to sensitivity proportional to dimensionality,
  \item[-] Red: LapMech with sensitivity $1$ in 2 dimensions and $2$ in higher dimensions, since it's equivalent to histogram problem 
  (posteriors of adjacent data sets differ only in two dimensions).
  \item[-] Blue: $\hexpmech$.
\end{itemize}
  Fig. \ref{fig_sampling} and Fig. \ref{subfig_prior} give us the average and 4-quantile of Hellinger distance between the sampled results and true posterior, by sampling for $10k$ times under each data size or prior configuration.

@@

Fig. \ref{subfig_concrete_prob_2d} and \ref{subfig_concrete_prob_3d} give us the discrete probabilities. On the x-axis: the distance of a potential output r from the true answer and on y-axis the probability of r being output by the mechanisms.
\begin{figure}[H]
\begin{center}
\centering
   \subfigure[2 dimensions with data size $100$]{
    \includegraphics[width=0.31\textwidth]{poster_4.eps}
  \label{subfig_prior}
  }
  \subfigure[2 dimensions with data size $600$]{
    \includegraphics[width=0.311\textwidth]{poster_5.eps}
  \label{subfig_concrete_prob_2d}
  }
  \subfigure[3 dimensions with data size $600$]{
    \includegraphics[width=0.311\textwidth]{poster_6.eps}
  \label{subfig_concrete_prob_3d}
  } 
\caption{4-quantile and discrete probability plots}
\label{fig_concrete_prob}
\end{center}
\end{figure}
\scriptsize{Experiments above are with unit prior $\betad(1,1), \betad(1,1,1)$ and $\betad(1,1,1,1)$ (except Fig. \ref{subfig_prior}) , balanced datasets, $\epsilon = 1.0$ and $\delta = 10^{-8}$.}
\end{block}

@@

\begin{itemize}
  \item[-] The smoothed Hellinger distance based exponential mechanism outperforms asymptotically the baseline 
  approach when the latter uses a sensitivity proportional to dimensionality.
  \item[-] Under the same data set size, $\hexpmech$ can outperform LapMech by increasing the prior.
  % \begin{enumerate}
  %   \item  The accuracy that we are going to explore next, and in a more principled and formal way.
